Tool-driven Revolutions in Archaeological Science

### 2018-12-18 analysis/paper/jcaa-paper.Rmd
Added quote of author guidelines about reproducibility.

We computed a comparison of word frequences in journal article titles in the Web of Science data to get a better understanding of what topics archaeologists are writing about when they cite R. First we separated the archaeology articles into two groups, those that cite R, and those that do not. Second, we filtered to keep only words that occur in titles in both groups, and removed stop words that are very common and uninformative (e.g. 'the', 'archaeological', 'study'). This resulted in `r prettyNum(nrow(frequency), ',')` words in `r prettyNum(nrow(archy_journal_articles))`. Third, for each word found in all the titles of the journal articles in each group, we computed its proportion of the total number of words in all the titles in each group. Figure \@ref(fig:text-mining-article-titles-archaeology-plot) shows the results of this analysis. Words near the red line are used with about equal frequencies by papers that cite R and by papers that do not cite R. Words far away from the red line are used much more by one group of articles compared to the other.

@@

@Touchon_McCoy_2016 had identified the use of scripting languages as being a factor for easily sharing methods and code, thereby increasing the rate of development of statistical methods. One notable practice that we observed during our bibliometric analysis is that among authors of articles citing R, a subset of these authors make publicly available the code and data that they used to generate the results presented in their article. We identified `r number_of_reproducible_articles` articles that include R script and data files, either in the supplementary materials or in a trustworthy data repository. Our contiunuously updated list of articles in this sample is available online here: https://github.com/benmarwick/ctv-archaeology. Figure \@ref(fig:archaeology-reproducible-articles-plot) shows that although this number is small, it is increasing, hinting at the emergence of a new approach to how archaeologists share their research.

>>>>

We computed a comparison of word frequences in journal article titles in the Web of Science data to get a better understanding of what topics archaeologists are writing about when they cite R. First we separated the archaeology articles into two groups, those that cite R, and those that do not. Second, we filtered to keep only words that occur in titles in both groups, and removed stop words that are very common and uninformative (e.g. 'the', 'archaeological', 'study'). This resulted in `r prettyNum(nrow(frequency), ',')` words in `r prettyNum(nrow(archy_journal_articles))` articles. Third, for each word found in all the titles of the journal articles in each group, we computed its proportion of the total number of words in all the titles in each group. Figure \@ref(fig:text-mining-article-titles-archaeology-plot) shows the results of this analysis. Words near the red line are used with about equal frequencies by papers that cite R and by papers that do not cite R. Words far away from the red line are used much more by one group of articles compared to the other.

@@

@Touchon_McCoy_2016 had identified the use of scripting languages as being a factor for easily sharing methods and code, thereby increasing the rate of development of statistical methods. One notable practice that we observed during our bibliometric analysis is that among authors of articles citing R, a subset of these authors make publicly available the code and data that they used to generate the results presented in their article. We identified `r number_of_reproducible_articles` articles that include R script and data files, either in the supplementary materials or in a trustworthy data repository. Our contiunuously updated list of articles in this sample is available online here: https://github.com/benmarwick/ctv-archaeology. Figure \@ref(fig:archaeology-reproducible-articles-plot) shows that although this number is small, it is increasing, hinting at the emergence of a new approach to how archaeologists share their research. The author guidelines of this very journal confirm this trend: "In the interests of open scholarship and the reproducibility of results, JCAA strongly encourages all authors to deposit material relating to their publication in a preservation repository"[@authorguidelines_JCAA].
